%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Luigi Timossi} \\ \vspace{1pt}
    Serra Ricco', Genoa \\ \vspace{1pt}
    \small \raisebox{-0.1\height} ~ \href{mailto:luigiestebant@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{luigiestebant@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/luigi-timossi-lurpigi/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/luigi-timossi-lurpigi}}  ~
    \href{https://github.com/Lurpigi}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Lurpigi}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Genoa}{Sept. 2023 -- March 2026}
      {Computer Science MSc - Computer Security and Engineering, 110 cum laude}{Genoa, Italy}
    \resumeSubheading
      {University of Genoa}{Sept. 2019 -- March 2023}
      {Computer Science BSc - Computer Science, 105}{Genoa, Italy}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Binary Analysis
                \item Digital Forensics
                \item Internet of Things
                \item Capstone Project
                \item Machine Learning
                \item Mobile Development
                \item Decentralized Systems
                \item Distributed Computing
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gruppo SIGLA}{September 2022 -- December 2022}
      {Curricular internship}{Genoa, Italy}
      \resumeItemListStart
        \resumeItem{Developed a full-stack solution for managing and controlling electric vehicle charging stations}
        \resumeItem{Implemented an SQL database following the OCPP protocol and a .NET backend for the API, with user and administrator login authentication}
        \resumeItem{Frontend developed in Angular, using state management, events, and styling libraries such as PrimeNG}
      \resumeItemListEnd

      \resumeSubheading
      {IREN}{June 2017 -- July 2018}
      {School-work alternance}{Genoa, Italy}
      \resumeItemListStart
        \resumeItem{The project won first prize in the national “Storie di Alternanza” competition and was honored in Rome}
        \resumeItem{Developed a series of static pages with games for "Città dei Bambini" of Genoa}
        \resumeItem{Implemented the pages using HTML, CSS and Javascript}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Master’s Thesis: LLMs to rank Decompilers} $|$ \emph{Python, Ghidra, CUDA, Docker, Java, C++}}{Sept. 2025 -- March 2026}
            \resumeItemListStart
            \resumeItem{Conducted a full empirical study on LLM-based decompiler assessment, combining quantitative perplexity metrics with qualitative judge evaluations.}
            \resumeItem{Created an automated pipeline to build a real-world benchmarking dataset from OSS-Fuzz projects for decompilation experiments.}
            \resumeItem{Built a comparison framework to evaluate decompiler outputs pairwise against source code using both blind and source-aware LLM judging.}
            \resumeItem{Implemented a Ghidra extension that sends decompiled function variants to an external LLM service and returns ranked outputs in the UI.}
            \resumeItemListEnd
        \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{StudyBuds Platform} $|$ \emph{Flutter, Node.js, TypeScript, PostgreSQL, Vue, Docker}}{October 2024 -- February 2025}
          \resumeItemListStart
            \resumeItem{Developed a cross-platform mobile application utilizing Flutter empowering university students to seamlessly find study buddies and form student groups.}
            \resumeItem{Developed a scalable backend REST API with Node.js, Express,TypeScript, Sequelize ORM and PostgreSQL  }
            \resumeItem{Integrated an academic SAML-based Single Sign-On and a custom Telegram bot for real-time notifications and group join links.}
            \resumeItem{Built a streamlined, reactive administrative dashboard employing Vue 3, Vite}
            \resumeItem{Architected the deployment utilizing Docker Compose, and Appium-driven environment for automated acceptance testing.}
          \resumeItemListEnd
        \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{IoT Smart Parking System} $|$ \emph{Node.js, Nuxt.js, PostgreSQL, MQTT, Node-RED, Docker, Wokwi}}{June 2025 -- July 2025}
          \resumeItemListStart
            \resumeItem{Architected an end-to-end IoT platform for smart parking reservations to optimize urban mobility, utilizing a microservices architecture deployed via Docker Compose.}
            \resumeItem{Developed a scalable backend REST API with Node.js, Express, and PostgreSQL to handle user authentication and reservations, paired with a Nuxt.js frontend featuring an interactive OpenLayers map.}
            \resumeItem{Implemented real-time gateway-to-cloud communication utilizing an MQTT broker to exchange JSON-based telemetry, health checks, and actuator commands with Wokwi-simulated hardware and Node.js virtual devices.}
            \resumeItem{Designed a real-time Node-RED dashboard to monitor the entire IoT ecosystem.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, TypeScript, JavaScript, SQL, HTML/CSS, PHP} \\
     \textbf{Frameworks \& Libraries}{: Node.js, Flutter, Vue.js, Angular, .NET, Express, Nuxt.js} \\
     \textbf{Tools \& Infrastructure}{: Docker, Git, CUDA, Linux, MQTT, Firebase, JUnit} \\
    }}
 \end{itemize}
 \vspace{-16pt}
 

%-----------INVOLVEMENT---------------

%\section{Leadership / Extracurricular}
%    \resumeSubHeadingListStart
%        \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%            \resumeItemListStart
%                \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%                \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%                \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%            \resumeItemListEnd
%        
%    \resumeSubHeadingListEnd


\end{document}
